---
title: "Clearing NA From PressGaneyRaw1T"
author: "Ankita Guha"
date: "October 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's load some of the libraries!

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(reader)
```

#Reading Dataframe and changing Data Type for subsequent analysis
```{r}
PressGaneyRaw <- read.csv("PressGaneyRaw1T.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
PressGaneyRaw$X = NULL

View(PressGaneyRaw)


library(lubridate)
#Date formatted according to the raw date type
PressGaneyRaw$AdmitDateLocal <- as.Date(ymd(PressGaneyRaw$AdmitDateLocal))
PressGaneyRaw$DischargeDateLocal <- as.Date(ymd(PressGaneyRaw$DischargeDateLocal))

PressGaneyRaw$SurveyCategoryID <- as.factor(PressGaneyRaw$SurveyCategoryID)
PressGaneyRaw$DomainID <- as.factor(PressGaneyRaw$DomainID)
PressGaneyRaw$QuestionID <- as.factor(PressGaneyRaw$QuestionID)
PressGaneyRaw$QuestionTypeID <- as.factor(PressGaneyRaw$QuestionTypeID)
PressGaneyRaw$QuestionTypeResponseID <- as.factor(PressGaneyRaw$QuestionTypeResponseID)
```

#Cleaning NA from PGResponseValue column
```{r}
#Clearing all the Rows Value that has NA in the PGResponseValue
PressGaneyRaw <- PressGaneyRaw[!is.na(PressGaneyRaw$PGResponseValue), ]

anyNA(PressGaneyRaw$PGResponseValue)
```

Okay, so our dataframe is cleaned from any NA values. 

In our next step, we are interested to find the Top Box Response value for all the Total Number Responses recorded by individual patient that is with unique FIN Number and also then see the *count* of the Total Top Box Responses which are *Yes* and the *count* of Total Top Box Response which are *No*. 

#Checking Just the FIN & the IsTopBox variable
```{r}
#Review the dataframe with the columns of interest
PressGaneyRaw %>% select(1,15)
```

#Calculate Total Number of Response And Number of TopBox that are Yes & No
```{r}
#Calculating the Total Number of Responses from each FIN number that means calculating the Total Number of Responses from each individual patients
library(dplyr)
PG <- PressGaneyRaw  %>% group_by(FIN) %>%
                         summarise(TotalResponse = n(), Yes = sum(IsTopBox==1), No = sum(IsTopBox==0))

PressGaneyRaw = join(PG, PressGaneyRaw, by=c("FIN"))


PressGaneyRaw <- subset(PressGaneyRaw, select = c(1,5:18,2:4))
```

Let's verify the total number of Unique FIN or unique patient response in the overall complete survey data. 

#Verification
```{r}
#Checking the total number of Unique FIN
PressGaneyRaw %>% group_by(FIN) %>% summarize(count=n())
```

So, total number of unique FIN is 20,623. And the dataframe that contains the cleaned PressGaney Patient Survey Data along with the TotalResponse, count of Yes and count of No as per unique FIN is PressGaneyRaw. 

```{r}
#Write the cleared File for subsequent analysis
write.csv(PressGaneyRaw, "PressGaneyRawCleaned.csv")
```

