---
title: "Data Wrangling 5"
author: "Ankita Guha"
date: "October 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's load some of the libraries, that we will need to explore the data:

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(reader)
```

Load some of the Data:
# Question Table
```{r}
QuestionT <- read.csv("Question.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
QuestionT = rename(QuestionT, ShortTextForQues = ShortText, LongTextForQues = LongText)

QuestionT$AAQIVarName = NULL
QuestionT$PGVarName = NULL

QuestionT$QuestionID <- as.factor(QuestionT$QuestionID)
QuestionT$QuestionTypeID <- as.factor(QuestionT$QuestionTypeID)
QuestionT$SurveyCategoryID <- as.factor(QuestionT$SurveyCategoryID)
```

# Domain Table
```{r}
DomainT <- read.csv("Domain.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
DomainT = rename(DomainT, LongTextForDomain = LongText)

DomainT$ShortText = NULL

DomainT$DomainID <- as.factor(DomainT$DomainID)
DomainT$SurveyCategoryID <- as.factor(DomainT$SurveyCategoryID)
```

#Domain + Question Table = (DQT)
```{r}
DQT = join(DomainT, QuestionT, by=c("SurveyCategoryID"))

DQT <- subset(DQT, select = c(2,1,3,4:8))
#PGPatientSatisfaction <- subset(PGPatientSatisfaction, select = c(1:6,8,7,9:13))

rm(DomainT)
rm(QuestionT)
```

# Question Type Table
```{r}
QuestionTypeT <- read.csv("QuestionType.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
QuestionTypeT = rename(QuestionTypeT, DescForQuesType = Description)
QuestionTypeT$Code = NULL

QuestionTypeT$QuestionTypeID <- as.factor(QuestionTypeT$QuestionTypeID)
```

# Question TypeResponse Table
```{r}
QuestionTypeRespT <- read.csv("QuestionTypeResponse.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
QuestionTypeRespT$X = NULL
QuestionTypeRespT$X.1 = NULL
QuestionTypeRespT$X.2 = NULL
QuestionTypeRespT$AAQIResponseValue = NULL

QuestionTypeRespT$QuestionTypeResponseID <- as.factor(QuestionTypeRespT$QuestionTypeResponseID)
QuestionTypeRespT$QuestionTypeID <- as.factor(QuestionTypeRespT$QuestionTypeID)
```

#QuestionTypeResponseT + QuestionTypeT = (QTRDT)
```{r}
QTRDT = join(QuestionTypeRespT, QuestionTypeT, by=c("QuestionTypeID"))
QTRDT$IsSkipLogicResponse = NULL

QTRDT <- subset(QTRDT, select = c(1:2, 6, 3:5))

rm(QuestionTypeRespT)
rm(QuestionTypeT)
```

# DQT + QTRDT = DQT
```{r}
DQT = join(DQT, QTRDT, by=c("QuestionTypeID"))
DQT$IsDefaultChoice = NULL
DQT$LongTextForQues = NULL

View(DQT)

DQT <- subset(DQT, select = c(1:4,6,5,8,7,9:11))
```


# Reading the PressGaneyRaw1.csv 
```{r}
PressGaneyRaw1T <- read.csv("PressGaneyRaw1.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
PressGaneyRaw1T$CAHPSID = NULL
PressGaneyRaw1T$SurveyId = NULL
PressGaneyRaw1T$HospitalNumber = NULL
PressGaneyRaw1T$Location = NULL
PressGaneyRaw1T$AdmittingADTID = NULL
PressGaneyRaw1T$AdmittingNPI = NULL
PressGaneyRaw1T$AttendingADTID = NULL
PressGaneyRaw1T$AttendingNPI = NULL
PressGaneyRaw1T$SkipLogicAppliedQuestionTypeResponseID = NULL
PressGaneyRaw1T$RecordedDateLocal = NULL


library(lubridate)
#Date formatted according to the raw date type
PressGaneyRaw1T$AdmitDateLocal <- as.Date(mdy(PressGaneyRaw1T$AdmitDateLocal))
PressGaneyRaw1T$DischargeDateLocal <- as.Date(mdy(PressGaneyRaw1T$DischargeDateLocal))

PressGaneyRaw1T$SurveyCategoryID <- as.factor(PressGaneyRaw1T$SurveyCategoryID)
PressGaneyRaw1T$DomainID <- as.factor(PressGaneyRaw1T$DomainID)
PressGaneyRaw1T$QuestionID <- as.factor(PressGaneyRaw1T$QuestionID)
PressGaneyRaw1T$QuestionTypeID <- as.factor(PressGaneyRaw1T$QuestionTypeID)
PressGaneyRaw1T$QuestionTypeResponseID <- as.factor(PressGaneyRaw1T$QuestionTypeResponseID)

rm(QTRDT)

```

#DQT + PressGaneyRaw1T in PressGaneyRaw1T

```{r}
#The final PressGaneyRaw1T contains the value of all the Patient Survey Data along with Response
PressGaneyRaw1T = join(PressGaneyRaw1T, DQT, by=c("SurveyCategoryID", "DomainID", "QuestionID", "QuestionTypeID", "QuestionTypeResponseID"))
#View(PressGaneyRaw1T)
rm(DQT)

PressGaneyRaw1T <- subset(PressGaneyRaw1T, select = c(1:6,10,7:9,11:15))
PressGaneyRaw1T <- subset(PressGaneyRaw1T, select = c(1:7,8,11,9,12,10,13:15))

write.csv(PressGaneyRaw1T, "PressGaneyRaw1T.csv")

```

# PG Response value gives the indication of the Patient Survey Rating
```{r}
PressGaneyRaw1T %>% filter(QuestionTypeID==1 & QuestionTypeResponseID==1)
```

### Before IPOC
##Filter by Year, Phase 1 (Anytime Before 2017)
# 30th June 2014 - 31st Dec 2016

```{r}
PressGaneyPhase1 <- PressGaneyRaw1T[PressGaneyRaw1T$AdmitDateLocal >= "2014-01-01" & PressGaneyRaw1T$AdmitDateLocal <= "2016-12-31",]
write.csv(PressGaneyPhase1, "PressGaneyPhase1.csv")
#rm(Phase1)
```

### During IPOC
##Filter by Year, Phase 2 (Jan - Mar 2017)
# 01st Jan 2017 - 31st Mar 2017

```{r}
PressGaneyPhase2 <- PressGaneyRaw1T[PressGaneyRaw1T$AdmitDateLocal >= "2017-01-01" & PressGaneyRaw1T$AdmitDateLocal <= "2017-03-31",]
write.csv(PressGaneyPhase2, "PressGaneyPhase2.csv")
#rm(Phase2)
```

### After IPOC
##Filter by Year, Phase 3 (April - Present Data)
# 1st Apr 2017 - 2018

```{r}
PressGaneyPhase3 <- PressGaneyRaw1T[PressGaneyRaw1T$AdmitDateLocal >= "2017-04-01" & PressGaneyRaw1T$AdmitDateLocal <= "2018-10-30",]
write.csv(PressGaneyPhase3, "PressGaneyPhase3.csv")
#rm(Phase3)
#View(Phase3)
```




















