---
title: "Data Preparation"
author: "Ankita Guha"
date: "October 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's load a few libraries we'll need:

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
#library(lubridate)
```


```{r reading patient survey data}
PGRaw <- read.table("PressGaneyRaw.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)

#summary(PGRaw)

str(PGRaw)
```

Let's convert the Dates from Factors to real Date for ease of analysis! 
P.S: While using the function as.Date always enter the date format as in the data provided, NOT as the format in which you want.

```{r characters to date}
library(lubridate)

ymd("20110604")

PGRaw$AdmitDateLocal <- as.Date(mdy(PGRaw$AdmitDateLocal))
PGRaw$DischargeDateLocal <- as.Date(mdy(PGRaw$DischargeDateLocal))
PGRaw$RecordedDateLocal <- as.Date(mdy(PGRaw$RecordedDateLocal))


PGRaw$SurveyCategoryID <- as.factor(PGRaw$SurveyCategoryID)
PGRaw$DomainID <- as.factor(PGRaw$DomainID)
PGRaw$QuestionID <- as.factor(PGRaw$QuestionID)
PGRaw$QuestionTypeID <- as.factor(PGRaw$QuestionTypeID)
PGRaw$SkipLogicAppliedQuestionTypeResponseID <- as.factor(PGRaw$SkipLogicAppliedQuestionTypeResponseID)


#PGRaw$AdmitDateLocal
#PGRaw$DischargeDateLocal
#PGRaw$RecordedDateLocal

```

For the sak of analysis we are going to ignore the attribute "QuestionTypeResponseID". So let's remove that column from our dataframe too. Let's check our final dataframe now after all the data type conversion.

```{r checking dataframe}
#Remove Column QuestionTypeResponseID 
PGRaw$QuestionTypeResponseID = NULL

#Check Dataframe
str(PGRaw)
```

 Yup, all the Dates Variables (such as: AdmitDateLocal, DischargeDateLocal, and RecordedDateLocal) are now converted to Date format, instead of Factors, which are used essentially for Categorical Variable.

```{r data overview}
head(PGRaw)
```

Looks like our one of the major attribute "FIN" in exponential format. Let's check it's class and try to fetch and view the value when called upon. 
```{r checking class and values of FIN}
class(PGRaw$FIN)

PGRaw$FIN
```

Let's check some of the Variables, before getting started. The FIN is the Patient ID Variable which gets a Unique ID number everytime a Patient gets admitted. Therefore, for a particular FIN, the AdmitDateLocal should generate a unique date. 

```{r check FIN & Admission Date}
# Checking both the distinct Patient Identification & Admission Date
PGRaw %>% distinct(FIN, AdmitDateLocal)

# Checking FIN Data with a Suspicious Value
PGRaw[PGRaw$FIN == 172000000000, ]
```

Filtering out the FIN from the Dataframe gives us an overview that for the FIN 172000000000, there are numerous AdmitDateLocal one dated in 2015 and another one in 2016 just from the first overview page. Clearly our data needs some cleaning before we proceed for analysis.

Even the duplicated Patient ID with the FIN 172000000000 has 7673 rows with the same Admission Date, which is not possible in real life. 

```{r viewing non-repeatatitive FIN}
subset(PGRaw, !duplicated(PGRaw$FIN))

#PGRaw %>% filter(FIN == 172000000000)  
```

Now, we have removed the duplicated FIN ID, however we still need to get read of all the FIN IDs  (with a trail of nine 0's behind) in our dataframe.
