---
title: "PGPhase2"
author: "Ankita Guha"
date: "October 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's load some of the libraries, that we will need to explore the data:

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(reader)
```

Load PressGaneyPhase2 Data:
```{r}
PGPhase2 <- read.csv("PressGaneyPhase2.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)

PGPhase2$X = NULL

library(lubridate)
#Date formatted according to the raw date type
PGPhase2$AdmitDateLocal <- as.Date(ymd(PGPhase2$AdmitDateLocal))
PGPhase2$DischargeDateLocal <- as.Date(ymd(PGPhase2$DischargeDateLocal))

PGPhase2$SurveyCategoryID <- as.factor(PGPhase2$SurveyCategoryID)
PGPhase2$DomainID <- as.factor(PGPhase2$DomainID)
PGPhase2$QuestionID <- as.factor(PGPhase2$QuestionID)
PGPhase2$QuestionTypeID <- as.factor(PGPhase2$QuestionTypeID)
PGPhase2$QuestionTypeResponseID <- as.factor(PGPhase2$QuestionTypeResponseID)
```

###Check patient's response based on QuestionTypeID, QuestionTypeResponseID & DomainID
#PG Response value gives the indication of the Patient Survey Rating
```{r}
PGPhase2 %>% filter(QuestionTypeID==1 & QuestionTypeResponseID==2) %>% with(DomainID==1) 


#Generates the Patient Survey Value that are already filled and removes the NA values for all the observations where the Response from patient is missing
PGPhase2NONA <- PGPhase2 %>% filter(!is.na(PGResponseValue)) #36,868
# PGPhase2 %>% filter(!is.na(PGResponseText)) #36,868
# PGPhase2 %>% filter(!is.na(DomainID)) #41,269
# PGPhase2  %>% filter(!is.na(LongTextForDomain)) #36,868
# PGPhase2  %>% filter(!is.na(QuestionID))#49,072
# PGPhase2  %>% filter(!is.na(QuestionTypeID))#49,072
# PGPhase2  %>% filter(!is.na(QuestionTypeResponseID))#42,517
#View(PGPhase2NONA)
```

###Filtering with different Question Types
##Discharge Information
```{r}
#For QuestionTypeID 1, & QuestionTypeResponseID 1, count of PGResponseValue 1 (Yes)
PGPhase2NONA %>% filter(QuestionTypeID==1, QuestionTypeResponseID==1) 
```
For Discharge related Information, pertaining to the Questions:
i) Whether Staff talked to the Patients when they left?
ii) If the Patient got information during their hospital stay! 
**1400** observations seems to have answered positively to these questions. 

```{r}
#For QuestionTypeID 1, QuestionTypeResponseID 2, count of PGResponseValue 2 (No)
PGPhase2NONA %>% filter(QuestionTypeID==1, QuestionTypeResponseID==2) 
```
**199** have answered the Discharge Related Questions negatively. 

##Overall Hospital Rating
```{r}
#For QuestionTypeID 2, QuestionTypeResponseID 3
PGPhase2NONA %>% filter(QuestionTypeID==2, QuestionTypeResponseID==12) 
```
Looks like **196** Patients voted for the Overall Hospital Rating as 9 which is a TopBox. 

```{r}
#For QuestionTypeID 2, QuestionTypeResponseID 13
PGPhase2NONA %>% filter(QuestionTypeID==2, QuestionTypeResponseID==13) 
```
**418** votes for the Overall Hospital Rating as 10, Best, which is also a TopBox.

## Different Kinds of Frequency Related Questions
```{r}
#For QuestionTypeID 3, QuestionTypeResponseID 17
PGPhase2NONA %>% filter(QuestionTypeID==3, QuestionTypeResponseID==17) 
```
**7893** Top Box answers for frequency related questions raised to this Patient Survey.

## Different Kinds of Qualitative Type Questions
```{r}
#For QuestionTypeID 4, QuestionTypeResponseID 22
PGPhase2NONA %>% filter(QuestionTypeID==4, QuestionTypeResponseID==22) 
```
**10,431** Top Box answers for all type of Qualitative answers. 

## Different Kinds of Surety Type Questions
```{r}
#For QuestionTypeID 5, QuestionTypeResponseID 26
PGPhase2NONA %>% filter(QuestionTypeID==5, QuestionTypeResponseID==26) 
```
**1005** for all the various Surety Questions Type

## Different Agreement Question Type
```{r}
#For QuestionTypeID 6, QuestionTypeResponseID 33
PGPhase2NONA %>% filter(QuestionTypeID==6, QuestionTypeResponseID==33) 
```
**820** positive response for all the various Agreement Question Type. 

## Different Questions Related to for Agreement related to No Meds
```{r}
#For QuestionTypeID 11, QuestionTypeResponseID 38
PGPhase2NONA %>% filter(QuestionTypeID==11, QuestionTypeResponseID==38) 
```
**461** positive responses for this category. 




