---
title: "RSW Patient Data"
author: "Ankita Guha"
date: "October 12, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's load some of the libraries

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
#library(lubridate)
```


```{r}
library("readxl")
RSWPData <- read_excel("RSW - Patient Data.xlsx")

str(RSWPData)
```

Let's convert our data type for ease of further analysis.

```{r converting Data Types}

# Converting some Data Types for ease of analysis
RSWPData$FIN <- as.numeric(RSWPData$FIN)
RSWPData$`Patient Type Cd-Desc` <- as.factor(RSWPData$`Patient Type Cd-Desc`) #Else keep it in character format if not used for further analysis

RSWPData$`Nurse Unit` <- as.factor(RSWPData$`Nurse Unit`)

RSWPData$`Discharge Disposition Code` <- sapply(RSWPData$`Discharge Disposition Code`, as.numeric)
RSWPData[, 'Discharge Disposition Desc'] <- lapply(RSWPData[, 'Discharge Disposition Desc'], factor)

RSWPData[, 'Principal Diagnosis Desc'] <- lapply(RSWPData[, 'Principal Diagnosis Desc'], factor)
RSWPData[, 'Phys Name - PHI'] <- lapply(RSWPData[, 'Phys Name - PHI'], factor)

View(RSWPData)

```

Okay, now that we have converted our data type, let's check if we have any duplicated values in FIN. FIN is the patient ID data and that should be unique across the whole column FIN. 

```{r number of rows & columns in our dataframe}
nrow(RSWPData)
ncol(RSWPData)

#Logical & Numeric Checking of Duplicated FIN 
any(duplicated(RSWPData$FIN))
anyDuplicated(RSWPData$FIN)

```

Looks like there are duplicated values in the FIN column and also we can see that the total number of duplicated FIN values are 67822! Let's now try to delete the duplicated FIN based on the last Physician Attended. 

## Identify & Remove Duplicated FIN
As per the requirement of the Project, we are required to remove the duplicated FIN, except the last instance within the duplicated batch.

```{r}
#Checking some data
library(dplyr)
RSWPData %>%
    distinct(FIN, `Phys Name - PHI`, .keep_all = FALSE)


# Figures out the duplicated FIN
duplicatedFIN <- data.frame(as.numeric(duplicated(RSWPData$FIN))) #creates df with binary var for duplicated FIN
colnames(duplicatedFIN) <- c("dupFIN")  #renames column for simplicity
RSWPDataNew <- cbind(RSWPData, duplicatedFIN) #bind to original dataframe RSWPData
df3 <- subset(RSWPData, duplicatedFIN == 1) #subsets df using binary var for duplicated

View(RSWPDataNew)


# Filters duplicated FIN
RSWPDataNew  %>%
   filter(dupFIN == 1)

which_dupFIN <- 1
filter_(RSWPDataNew, ~dupFIN == which_dupFIN)


#Reading into a new dataframe 
RSWPDataFinal <- RSWPDataNew[!rev(duplicated(rev(RSWPDataNew$FIN))),]
View(RSWPDataFinal)

#Frees some memory space for us
#rm(df3, RSPWDataNew)

#Recheck if we have removed all the duplicated FIN from our new dataframe
any(duplicated(RSWPDataFinal$FIN))

```

Since we got some duplicated values. Let's create a subset of our dataframe that shows which FIN have duplicated values. If the FIN has a duplicated value, it takes a value of 1, else it assigns a value of 0. So, now we can look at the dataframe, RSWPDataNew and can check which rows for FIN contains duplicated value. As per the requirement of the Project we need to remove the duplicated FIN, except for the last instance. As we can see,from our codes above our final dataframe, RSPWDataFinal, is a cleaned of duplicated FIN. 

Now that we have removed all the duplicated values of Patient ID, FIN Number. Let's get rid of the last column and write the file to retain for further analysis.
```{r}
# Removes the checking column variable
RSWPDataFinal$dupFIN <- NULL

#Write the cleaned file for further analysis
rm(df3)
rm(duplicatedFIN)
rm(RSWPData)
rm(RSWPDataNew)
rm(which_dupFIN)

#Write file for further analysis
write.csv(RSWPDataFinal, "RSWPDataCleaned.csv")
```

